Validation of Visual Statistical Inference, Applied to Linear Models

### 2012-06-06 paper_jasa.tex
comments updated

The actual data plot is generated by making a scatterplot of $Y$ vs $X_1$ with the least squares regression line overlaid. To produce the null plots in the lineup null data was simulated from $N(X \hat{\beta}, {\hat{\sigma}}^2$) and plotted using the same scatterplot method as the actual data. 
An example lineup from this experiment is shown in Figure \ref{fig:test_continuous}.  This lineup is generated using sample size ($n$)=100, slope($\beta$)=1.25 and and error SD($\sigma$)=5. The actual data plot location is 11. \green{Check this} This lineup, we think, is a difficult one. To select 10 lineups for a subject, each combination of sample size ($n$) and error SD ($\sigma$) is given a difficulty value based on the slope ($\beta$) parameters. For the smallest slopes the difficulty is 0 (hardest) and for the largest slopes the difficulty is 4 (easiest). For one combination of sample size and standard deviation, the subject sees a randomly selected lineup of each difficulty level, all the slopes, giving 5 lineups. Another four lineups are chosen from a second choice of sample size and standard deviation, with difficulty levels 0-3, and the last lineup shown was a randomly selected lineup with difficulty 0. The order that the lineups are shown to participants is randomized.\blue{The order is as described not randomized after. The randomization is done picking first combination of sample size and sd as well as picking lineups for each combination of parameter} \green{Is this a correct description of the procedure?} Each subject saw a substantial number of difficult lineups. The intention was noble, to get a better handle on the power of the lineups for small slopes, but practically this made is very tiring for the participants. It would be better to provide the subjects with a larger selection of easier lineups and just a few difficult ones. \green{perhaps should go into so much detail about this, or keep this for the conclusions section.}

@@

Five replications of actual data sets for each slope value shown in Table \ref{tbl:experiment_params}, producing 30 lineups. Six groups of difficulty level based on slope are defined, difficulty = 0 for largest slope and difficulty = 5 for the smallest slope.  \green{This is the reverse of the previous experiment}  Eight (8) lineups with two from each of the difficulty group from 0 through 3 and two(2) lineups with one from each difficulty group 4 and 5 were randomly picked for each subject.

>>>>

The actual data plot is generated by making a scatterplot of $Y$ vs $X_1$ with the least squares regression line overlaid. To produce the null plots in the lineup null data was simulated from $N(X \hat{\beta}, {\hat{\sigma}}^2$) and plotted using the same scatterplot method as the actual data. 
An example lineup from this experiment is shown in Figure \ref{fig:test_continuous}.  This lineup is generated using sample size ($n$)=100, slope($\beta$)=1.25 and and error SD($\sigma$)=5. The actual data plot location is 11. \green{Check this} This lineup, we think, is a difficult one. To select 10 lineups for a subject, each combination of sample size ($n$) and error SD ($\sigma$) is given a difficulty value based on the slope ($\beta$) parameters. For the smallest slopes the difficulty is 4 (hardest) and for the largest slopes the difficulty is 0 (easiest). For one combination of sample size and standard deviation, the subject sees a randomly selected lineup of each difficulty level, all the slopes, giving 5 lineups. Another four lineups are chosen from a second choice of sample size and standard deviation, with difficulty levels 0-3, and the last lineup shown was a randomly selected lineup with difficulty 0. The order that the lineups are shown to participants is randomized.\blue{The order is as described not randomized after. The randomization is done picking first combination of sample size and sd as well as picking lineups for each combination of parameter} \green{Is this a correct description of the procedure?} Each subject saw a substantial number of difficult lineups. The intention was noble, to get a better handle on the power of the lineups for small slopes, but practically this made is very tiring for the participants. It would be better to provide the subjects with a larger selection of easier lineups and just a few difficult ones. \green{perhaps should go into so much detail about this, or keep this for the conclusions section.}

@@

Five replications of actual data sets for each slope value shown in Table \ref{tbl:experiment_params}, producing 30 lineups. Six groups of difficulty level based on slope are defined, difficulty = 0 for largest slope and difficulty = 5 for the smallest slope.    Eight (8) lineups with two from each of the difficulty group from 0 through 3 and two(2) lineups with one from each difficulty group 4 and 5 were randomly picked for each subject.
